---
title: "p8105_hw5_yl4928"
author: "Rachel"
date: "11/16/2021"
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1 

Raw data 

```{r, message = FALSE}
homicideraw_df = read_csv("./homicide-data.csv")
```
##Describe the raw data

The `homicideraw_df` dataset contains `r nrow(homicideraw_df)` observations and `r ncol(homicideraw_df)` variables. 


Read in the data.

```{r, message = FALSE}
homicide_df = 
  read_csv("./homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```
# Describe the raw data 




```{r, message = FALSE}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r, message = FALSE}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r, message = FALSE}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r, message = FALSE}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled
  n_total
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("./homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```

## Problem 2

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

# 2.1 Start with a dataframe containing all file names
# 2.2 Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
# 2.3 Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary


```{r, message = FALSE}
allnames_df = tibble(files = list.files("./data"))
```

```{r, message = FALSE, error = TRUE}
path_df = 
  allnames_df %>% 
  tibble(
    path = list.files("./data"),
  ) %>% 
  mutate(
    path = str_c("data/", path),
    data = map(path, read_csv)
  )
```

```{r, message = FALSE}
tidy_path_df = 
  path_df %>%
  separate(files, into = c("arm", "subjectID")) %>% 
  select(arm, subjectID, data) %>% 
  unnest(data) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "result_data"
  )
```

## Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r, fig.width = 8}
tidy_path_df %>% 
  mutate(
    arm = recode(
      arm, 
      con = "control",
      exp = "experiment"
    )
  ) %>% 
ggplot(aes(x = week, y = result_data, group = subjectID, color = subjectID)) + 
  geom_line() + 
  facet_grid(.~arm) 

```

## Problem 3 

```{r, message = FALSE}
library(tidyverse)

set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```
Fill in the missing values 
# Write a function 
```{r, message = FALSE}
fill_in = function(x) {
 if (is.numeric(x)) {
   x = ifelse(is.na(x),
 mean(x, na.rm = TRUE), x)}
  
 else{x = ifelse(is.na(x), "virginica", x)}
}

```

## Apply the function 
```{r, message = FALSE}
output = map(iris_with_missing, fill_in)

bind_rows(output)
  
```

